Exercise 1: Software Architecture Description of the HS07 System

### 2008-02-04 trunk/SAiP/Module1/H1/doc/paper.tex
Date hardcoded :(
More discussion detail

\date{$Date$}

@@

% =====================================================================
\section{Discussion}
$<<$What are the strengths and limitations of this approach to
architectural description judging from this case?$>>$

$<<$Are there aspects of the software architecture that have not been
properly described?$>>$

$<<$...$>>$

>>>>

\date{2008-02-04 13:32}

@@

% =====================================================================
\section{Discussion}
\subsection{Strength and Limitations of the approach}
$<<$What are the strengths and limitations of this approach to
architectural description judging from this case?$>>$

When using the approach described in \cite{christensen2004archdesc} with reverse 
engineering to achieve an architectural description, the dangers posed seem to 
be finding the correct balance in the choice of detail level. It
is easy to get to much information, cluttering the purpose of the 
AD, which in a basic sense is to clarify and present at wider understanding of
the system.

Experienced architects might recognize patterns emerging from the process, and 
immediately see possible design flaws in the implementation of these, thus
being able to help improve the quality of any evolving system.

The purpose of doing a reverse engineered AD must either be to evolve
the system of to extract clarification. Care should be taken to achieve either
goal. 
\subsection{Whats missing?}
$<<$Are there aspects of the software architecture that have not been
properly described?$>>$
Stakeholders and their concerns. This encompasses both users/aquirers and developers. We also need to discuss the feasibility and maintainablity of the system.

\subsection{IEEE Conformance}

$<<$For the architectural description above, discuss what (if anything) should be changed or added for it to comply with the IEEE recommended practice for architectural description$>>$

The following are the problems identified in order to comply with \cite{ieeerecommendedpractice}.

Clause 5.2: The stakeholders and their precise concerns need to be identified for each view.

Clause 5.5: Consistency checks across all existing views.

\subsection{Perry \& Wolf Considerations}
$<<$Consider the definition of software architecture by [Perry and Wolf, 1992]. Discuss what the 'elements', 'form', and 'rationale' according to this definition would be for the HS07 system$>>$

\cite{perrywolf1992} defines "elements" as three different classes, data elements, processing elements and connecting elements. In HS07 the data elements are temperatures, the processing element is the gateway and the connecting element is HTTP. The "form", as described by Perry and Wolf, is the choice of the observer pattern in HS07, and the "rationale" for doing so are defined by the Achitectural Requirements described elsewhere in this document.
